Supplementary: A temporal network analysis of drug co-prescription around antidepressants and anxiolytics uses in the Netherlands from 2018 to 2022

### 2025-12-15 docs/submission/GEPI/supplementary-revision-01/supplementary.tex
Track the revision and its diff

>>>>

\subsection{Exploring seasonality in the
dataset}\label{exploring-seasonality-in-the-dataset}

Exploration on seasonality was done on detrended daily and weekly data
by generating seasonal plots and calculating the autocorrelation (ACF)
and partial autocorrelation function (PACF). Seasonal plots were
generated for weekly and yearly pattern by using daily and weekly data,
respectively. To generate the seasonal plots, the data was first
deconstructed based on its period. For daily data, the weekly period was
used; while for weekly data, the yearly period was used. The weekly
period was obtained by creating an ordered value formatted as year -
week, e.g.~\texttt{2018\ -\ W01}. Similarly, monthly period was obtained
by creating an ordered value formatted as year - month,
e.g.~\texttt{2018\ -\ M01}. We then grouped the series by its
deconstructed period and visually examine seasonality as overlapping
pattern in most periods. To substantiate the findings, ACF and PACF
plots were used to check on statistical significance of a given pattern.
